%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deemweaver}
\usepackage{fancyhdr}
\usepackage{amsmath} 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Raphael}{Deem}{\urlstyle{same}\href{mailto:raphael.deem@gmail.com}{raphael.deem@gmail.com} | \href{tel:15037408347}{503.740.8347}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.32\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
{\FA \faGithub} \href{https://github.com/r0fls}{\bf r0fls} \\
{\FA \faLinkedin} \href{https://www.linkedin.com/in/raphael-deem-5757ba31}{\bf Raphael Deem} \\
{\FA \faStackOverflow}  \href{http://stackoverflow.com/users/1318734/rofls}{\bf r0fls} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Advanced:}
Python\textbullet{}Go\textbullet{}Javascript\\
\location{Intermediate:}
SQL\textbullet{}BASH\textbullet{}Ruby\textbullet{}C++\textbullet{}C\\
HTML/CSS\textbullet{}Android\textbullet{}Java\\
\location{Familiar:}
PHP \textbullet{}R
\sectionsep
\subsection{CI/CD Systems}
{}Gitlab \textbullet{} Travis\textbullet{}Jenkins
\sectionsep
\subsection{Monitoring \& Alerting}
Prometheus\textbullet{}Grafana\textbullet{}Pagerduty
\sectionsep
\subsection{Miscellaneous}
Linux\textbullet{}Kubernetes\textbullet{}Docker

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Reed College}
\descript{BA in Mathematics}
\location{May 2010 | Portland, OR}
Produced thesis covering \\ error-correcting codes used in communications engineering.
\sectionsep

\subsection{De La Salle \protect\\ North Catholic}
\location{May 2005 | Portland, OR}
Funded tuition for four years by participating in an experimental,
immersive work study program. \\First graduating class.
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\href{https://github.com/huge-success/sanic}{\bf Sanic} (maintainer): python3 asynchronous web-framework modeled from Flask.\\
\vspace{3pt}
\href{https://github.com/r0fls/gostats}{\bf Gostats} (creator): golang package for generating random numbers from non-unified distributions. \\
\vspace{3pt}
\href{https://github.com/kubernetes-sigs/aws-alb-ingress-controller}{\bf alb-ingress-controller} (developer): golang ingress controller utilizing AWS ALBs; official LB for EKS.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ABOUT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{About}
I am a systems and backend engineer, and a golang and python afficianado. I enjoy working with kubernetes and containers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Ticketmaster}
\descript{| Systems Engineer III}
\location{May 2017 - Present | Remote}
\begin{tightemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Architected and engineered system for attributing kubernetes workload costs to product teams, using prometheus, golang and the spotinst API.
\item Designed and created end-to-end tests to verify kubernetes cluster functionality and report on SLAs, using golang, bash, and prometheus.
\item Deployed the upstream nginx-ingress-controller as a cost-saving alternative to our internally developed alb-ingress-controller, using helm and gitlab ci/cd.
\end{tightemize}
\sectionsep


\runsubsection{Platform.sh}
\descript{| Infrastructure Engineer}
\location{May 2016 - May 2017 | Remote}
\begin{tightemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Automated deployment of high-availability enterprise clusters, using python fabric and mako templates.
\item Created command line tool for managing fastly CDN services.
\item Added support for Postgresql high availability clusters, using puppet and bidirectional replication.
\end{tightemize}
\sectionsep


\runsubsection{Sellerengine Software}
\descript{| Automation Engineer}
\location{Mar 2015 - May 2016 | Portland, OR}
\begin{tightemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Automated daily upload of sales and return data to our accounting system using Python.
\item Developed software to extract and process bi-weekly payroll data using Python and PostgreSQL.
\item Influenced and designed accounting methodology and techniques.
\end{tightemize}
\sectionsep

\runsubsection{Your Supply Company}
\descript{| CTO}
\location{Aug 2014 – Sep 2015 | Portland, OR}
\begin{tightemize}
\item Designed and hosted website (\href{http://yoursupply.co}{\bf yoursupply.co}) using Apache, Linux and Bootstrap CSS.
\item Wrote and deployed python scripts to scrape listing data from Amazon.
\end{tightemize}
\sectionsep


\runsubsection{Huron Consulting}
\descript{| SQL Developer}
\location{Oct 2013 – Aug 2014 | Lake Oswego, OR}
\begin{tightemize}
\item Implemented and customized bolt-on software for healtcare information systems.
\end{tightemize}
\sectionsep

\runsubsection{Dunthorpe Marketing}
\descript{| Data Specialist }
\location{Mar 2013 – Oct 2013 | Portland, OR}
\begin{tightemize}
\item Automated weekly reporting of SalesForce metrics using Visual Basic and the SalesForce API.
\end{tightemize}
\sectionsep

\runsubsection{Stream Global Services}
\descript{| Networking Specialist}
\location{Oct 2011 – Mar 2013 | Beaverton, OR}
\begin{tightemize}
\item Used traceroute, ping, and other command line tools to troubleshoot issues with internet connectivity.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Research}
%\runsubsection{Cornell Robot Learning Lab}
%\descript{| Researcher}
%\location{Jan 2014 – Jan 2015 | Ithaca, NY}
%Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.
%\sectionsep
%
%\runsubsection{Cornell Phonetics Lab}
%\descript{| Head Undergraduate Researcher}
%\location{Mar 2012 – May 2013 | Ithaca, NY}
%Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research.
%\sectionsep
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{SELECT OSS CONTRIBUTIONS AND OTHER}
%\begin{tabular}{rll}
%2016    & Djstripe      & Stripe integration for Django. \\
%2015    & Agate	        & Open source data visualisation library written in Python.\\
%\end{tabular}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\end{document}  \documentclass[]{article}
